Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-24 Manuscript/FLPhish(Trans).tex
增加更多参考文献，填到满12页

\section{Introduction}
\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the online shopping app users' purchase record data, patients' clinical data and etc. Developers get a large-scale data from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

@@

\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system. Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet}. Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers. Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference for determining a client's level of trust. We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment reveal that FLPhish performs admirably against Byzantine attacks. Even when confronted with very non-IID distributions and high fractions of Byzantine clients, FLPhish outperforms FedAvg and Ensemble FL significantly.
\par Our future work will evaluate FLPhish against more advanced Byzantine attacks and improve our framework based on the evaluation results.

>>>>

\section{Introduction}
\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the online shopping app users' purchase record data, patients' clinical data and etc. Developers get a large-scale data from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_01_GoogleFL,ref_02_FLConcept,li2021a}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp, hao2020hao}.

@@

\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system. Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet, wang2019beyond}. Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers \cite{miao2018attack, laishram2016curie}. Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data,yang2017generative,sun2018data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

@@

In this paper, we have designed an FL architecture, Ensemble Federated Learning in this study, which allows us to use the unlabeled dataset to transfer knowledge between the FL server and FL clients. We have crafted the FLPhish technique to make Ensemble FL resistant to Byzantine attacks by using a labeled dataset as `bait' to detect malicious Byzantine clients. Furthermore, we have proposed a reputation technique based on Bayesian inference for determining a client's level of trust. We have also presented two aggregation techniques, FLPhish-threshold and FLPhish-weight, to improve FLPhish's performance. At last, we have tested our suggested FLPhish in a variety of scenarios. The results of the experiment demonstrates the comparable performance of FLPhish in terms of accuracy and robustness under Byzantine attacks in FL. 
\par Our future work will focus on evaluating FLPhish against more advanced Byzantine attacks and improving FLPhish scheme's efficiency.
